Assessing rigor and impact of research software for hiring and promotion in psychology: A comment on Gärtner et al.~(2022)

### 2023-10-04 manuscript.Rmd
make contributions a list

The authors made the following contributions.
Andreas M. Brandmaier: Conceptualization, Writing - Original Draft Preparation, Writing - Review & Editing, Supervision;
Maximilian Ernst: Conceptualization, Writing - Original Draft Preparation, Writing - Review & Editing;
Aaron Peikert: Conceptualization, Writing - Original Draft Preparation, Writing - Review & Editing.

>>>>

The authors made the following contributions.
Andreas M. Brandmaier
: Conceptualization, Writing - Original Draft Preparation, Writing - Review & Editing, Supervision;
Maximilian Ernst
: Conceptualization, Writing - Original Draft Preparation, Writing - Review & Editing;
Aaron Peikert
: Conceptualization, Writing - Original Draft Preparation, Writing - Review & Editing.
